Analysis of bulk void regions

### 2014-05-01 cosmic_voids.tex
Analysis of the distribution of density vs L1

@@

>>>>

%-------------------------------------------------------------------------
\subsection{Fractional anisotropy as tracer of the cosmic web}
\label{subsec:FA_web}
%-------------------------------------------------------------------------

@@

For the distribution of the density with respect to the $\lambda_1$ 
eigenvalue, it can be appreciated an analogous behaviour, where central 
regions of voids present the most under-dense values of the overall cosmic 
web. For outer layers of voids, the density field grows progressively 
until sheets and filaments are reached. However, the dispersion in the 
distributions indicates that the geometry of voids as quantified by both 
web schemes is not compatible with the density field, i.e. contours of the
$\lambda_1$ eigenvalue do not coincide with contours of the density field. 
Then, the density is not a reliable quantity to be used as tracer of voids. 
Furthermore, another advantage of using the FA index instead of the 
density is the non-monotonous behaviour of the FA median value, with a 
local maximum that allows to identify the boundaries of void regions.
